Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
brush up a comment.
adding a comment.

\begin{quote}
    \emph{sol: Can we remove what follows??}
    \emph{kazu: I want to keep them for readability??}
\end{quote}

@@

    kazu: ``behavior'' sounded strange at least to me at the first time.
    We alreay supported this word with typeclassopedia. So, I think
    this paragraph is completed.

@@

\begin{quote}
    sol: remove?

>>>>

\begin{quote}
    \emph{sol: Can we remove what follows??}\\
    \emph{kazu: I want to keep them for readability.}
\end{quote}

@@

    kazu: ``behavior'' sounded strange at least to me at the first time.
    We alreay supported this word with typeclassopedia. So, I think
    this paragraph is completed. Should we replace ``is associated'' with
    ``might be associated''?

@@

\begin{quote}
    sol: remove?
    kazu: yes. But I would add a sentence such as ``This section
    will discuss problems when we try to use these tools for BDD''.
